---
title: "Histology Analysis"
author: "Justin Varholick"
date: "2024-02-08"
output: html_document
---
# packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)

library(ggbeeswarm)
library(ggbreak)
library(patchwork)
library(stringr)
library(cowplot)
library(ggsci)
library(see)
library(svglite)
library(extrafont)

library(easystats)
library(lme4)
library(lmerTest)
library(FSA)
```


# import data
```{r}
measures <- read_excel("data/measurements_020924.xlsx")
daystoclose <- read.csv("data/EarDaysToClose_Data.csv")
muscle <- read.csv("data/muscle.csv")
hairs <- read_excel("data/hairfollicles.xlsx")
```

# data wrangling
## make data neat
```{r}
measures <- measures %>% 
  select(AnimalID, Slide, Name, Num.points, Length_microm) %>% 
  left_join(daystoclose[,c(2,3,7,8)]) %>% 
  mutate(AgeInMonths = (AgeAtInjury/30.417))

measures$AgeCat[is.na(measures$AgeCat)] <- "Uninj. Tissue"
measures$AgeCat <- factor(measures$AgeCat, levels = c("Uninj. Tissue", "3-4mo", "4-6mo", "6-9mo", "≥ 22mo"))

muscle <- muscle %>% 
  filter(uninj.muscle == 1)
```
## make data for depth of injury
```{r}
##Count the number of slides per animalid, 

slidecount <- measures %>% 
  filter(Name == "Regenerated Length") %>% 
  group_by(AnimalID) %>% 
  summarise(slidecount = n())

#assign a count to each slide number, 

measures1 <- left_join(measures, slidecount, by = "AnimalID")

#divide count by number of slides per animal id, 

slidenumber <- measures1 %>% 
  filter(Name == "Regenerated Length") %>% 
  group_by(AnimalID) %>% 
  mutate(Slide_adj = rank(Slide)) %>% 
  select(AnimalID, Slide, Slide_adj, slidecount) %>% 
  unique() %>% 
  mutate(Slide_per = 100*(Slide_adj/slidecount))

measures2 <- left_join(measures1, slidenumber, by = c("AnimalID", "Slide", "slidecount"))
```

## make individual data sets for each metric
**for graphing**
```{r}
cartilage <- measures2 %>% 
  filter(Name == "Cartilage Length") %>% 
  group_by(AnimalID, Slide, Slide_per, Sex, AgeInMonths, AgeCat, Name) %>% 
  summarise(Length = sum(Length_microm), Count = n())
  #summarise(Area = sum(Area.µm.2), Perimeter = sum(Perimeter.µm))

regenarea <- measures2 %>% 
  filter(Name == "Regenerated Length") %>% 
  group_by(AnimalID, Slide, Slide_per, Sex, AgeInMonths, AgeCat, Name) %>% 
  summarise(Length = sum(Length_microm), Count = n())

adipocytes <- measures2 %>% 
  filter(Name == "Adipocytes") %>% 
  group_by(AnimalID, Slide, Slide_per, Sex, AgeInMonths, AgeCat, Name) %>% 
  summarise(count = sum(Num.points))

cartregen <- cartilage %>% 
  left_join(regenarea, by = c("AnimalID", "Slide", "Slide_per", "Sex", "AgeInMonths", "AgeCat")) %>% 
  mutate(perc_cartregen_length = 100*(Length.x / Length.y))

adiporegen <- adipocytes %>% 
  left_join(regenarea, by = c("AnimalID", "Slide", "Slide_per", "Sex", "AgeInMonths", "AgeCat")) %>% 
  mutate(count_area = count / (Length/100))

cartregen$AnimalID_Slide <- paste(cartregen$AnimalID, cartregen$Slide, sep = "-")

muscleregen <- muscle %>% 
  left_join(regenarea, by = c("AnimalID", "Slide")) %>% 
  mutate(count_area = fiber.count / (Length/100)) %>% 
  filter(!is.na(count_area))#############lots of NA values, why?

hairregen <- hairs %>% 
  left_join(regenarea, by = c("AnimalID", "Slide")) %>% 
  mutate(count_area = Num.points / (Length/100)) %>% 
  filter(!is.na(count_area))#############lots of NA values, why?

```

## make tables of mean values
**for graphing and analysis**
```{r}
cartregen_means <- cartregen %>% 
  group_by(AnimalID, AgeCat) %>% 
  summarise(mean_perc_cartregen_length = mean(perc_cartregen_length), mean_count=mean(Count.x))

adipo_means <- adiporegen %>% 
  group_by(AnimalID, AgeCat) %>% 
  summarise(mean_count_area=mean(count_area), mean_count=mean(count))

muscle_means <- muscleregen %>% 
  group_by(AnimalID, AgeCat) %>% 
  summarise(mean_count_area=mean(count_area), mean_count=mean(fiber.count))

hairs_means <- hairregen %>% 
  group_by(AnimalID, AgeCat) %>% 
  summarise(mean_count_area=mean(count_area), mean_count=mean(Num.points))
```
# Analysis
## cartilage % mean tables
```{r}
cartregen_means2 <- cartregen_means %>% 
  mutate(AgeCat2 = case_when(AgeCat == "Uninj. Tissue" ~ "Uninjured",
                             AgeCat == "Injured at 3-4mo" ~ "Injured",
                             AgeCat == "Injured at 4-6mo" ~ "Injured",
                             AgeCat == "Injured at 6-9mo" ~ "Injured",
                             AgeCat == "Injured at ≥ 22mo" ~ "Injured")) %>% 
  group_by(AgeCat2) %>% 
  summarise(mean2_perc_cartregen_length = mean(mean_perc_cartregen_length), mean2_count = mean(mean_count))

cartregen_means3 <- cartregen_means %>% 
  group_by(AgeCat) %>% 
  summarise(mean3_perc_cartregen_length = mean(mean_perc_cartregen_length), mean3_count = mean(mean_count))
```

## cartilage % graph
```{r}
cartregen_means <- cartregen_means %>% 
    mutate(AgeCat2 = case_when(AgeCat == "Uninj. Tissue" ~ 1,
                             AgeCat == "3-4mo" ~ 0,
                             AgeCat == "4-6mo" ~ 0,
                             AgeCat == "6-9mo" ~ 0,
                             AgeCat == "≥ 22mo" ~ 0))


cmeansplot <- ggplot(cartregen_means, aes(AgeCat, mean_perc_cartregen_length)) +
  geom_bar(aes(fill = AgeCat), fun = "mean", stat = "summary", alpha = 0.8, width = 0.75) +
  #geom_bar(fun = "mean", stat="summary", color = "black", alpha = 0.85) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  geom_point2(size = 2, alpha = 0.6, color = "black") +
  ylab("Mean % \nCartilage in ROI") + xlab("") +
  #scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), limits=c(0,100), labels=function(x) paste0(x,"%")) +
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") +
  theme(legend.position = "none", axis.text.x=element_text(angle=45, vjust = 1, hjust = 1))
cmeansplot
ggsave("Figures/CartilagePercent.pdf", width=40, height=45, unit="mm", dpi = 300)
#ggsave("Figures/CartilagePercent.eps", dpi=300, width=180, height=90, unit="mm")
```
## cartilage % analysis
```{r}
#oneway anova, taking the mean percentage for each animal across all slides/positions
res_aov <- aov(mean_perc_cartregen_length ~ AgeCat, data = cartregen_means)
summary(res_aov)
report(res_aov)
TukeyHSD(res_aov)
plot(TukeyHSD(res_aov))
```
## cartilage position (proximal, middle, distal) graph
```{r}
cartregen2 <- cartregen %>% 
  mutate(Position = case_when(Slide_per <= 33.333 ~ "Proximal",
                              Slide_per > 33.333 & Slide_per < 66.666 ~ "Middle",
                              Slide_per >= 66.666 ~ "Distal")) %>% 
  mutate(Position_Age = paste(AgeCat, Position, sep = "-")) %>%
  filter(AgeCat != "Uninj. Tissue")
cartregen2$Position <- factor(cartregen2$Position, levels = c("Proximal", "Middle", "Distal"))
cartregen2$Position_Age <- factor(cartregen2$Position_Age, levels = c("≥ 22mo-Proximal", "≥ 22mo-Middle", "≥ 22mo-Distal",
                                                              "3-4mo-Proximal", "3-4mo-Middle", "3-4mo-Distal",
                                                              "4-6mo-Proximal", "4-6mo-Middle", "4-6mo-Distal",
                                                              "6-9mo-Proximal", "6-9mo-Middle", "6-9mo-Distal"))

#supplemental graph
cposplot <- ggplot(cartregen2, aes(AgeCat, perc_cartregen_length)) +
  geom_boxplot_pattern(aes(pattern_density = Position, fill = AgeCat),
                       pattern = "circle", pattern_spacing = 0.02, pattern_fill = "black", color = "black") +
  #geom_bar(fun = "mean", stat="summary", position = "dodge", color = "black", alpha = 0.85) +
  #stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  #geom_point2(size = 2, alpha = 0.5, position = position_dodge(width=.9)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), limits=c(0,110), breaks = c(0, 25, 50, 75, 100), labels=function(x) paste0(x,"%")) +
  ylab("% Cartilage in ROI") + xlab("") +
  guides(color = "none") +
  scale_fill_manual(values = c("#FDE725", "#22A884", "#414487", "#440154")) +
  theme_cowplot() + theme(legend.position = "none")
cposplot

cposplot2 <- ggplot(cartregen2, aes(Position, perc_cartregen_length, color = AgeCat, group = AgeCat)) +
  stat_summary(geom = "line", fun = "median", position = position_dodge(width = 0.2), linetype = "dashed") +
  stat_summary(fun.min = function(z) { quantile(z,0.25) },
  fun.max = function(z) { quantile(z,0.75) },
  fun = median, position = position_dodge(width = 0.4), shape = 3, size = 1) +
  geom_point2(size = 2, alpha = 0.6, position = position_dodge(width = 0.4)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), limits=c(0,110), breaks = c(0, 25, 50, 75, 100), labels=function(x) paste0(x,"%")) +
  ylab("% Cartilage in ROI")  + xlab("") + labs(color = "Age \nat Injury") +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") + theme(legend.position = "none")
cposplot2
ggsave("Figures/CartilagePercent_position.pdf", width=80, height=45, unit="mm", dpi = 300)
```
```{r}
ggplot(cartregen, aes(Slide_per, perc_cartregen_length, color = AgeCat)) +
  geom_point() +
  facet_wrap(~AnimalID)
```


## cartilage position analysis
```{r}
#repeated measures anova can't be run because the data is unbalanced, so we run a mixed model
# this model is with slide as a percentage
cper.base <- lmer(perc_cartregen_length ~ Slide_per + (Slide_per | AnimalID), data = cartregen2, control=lmerControl(optimizer="bobyqa"))

cper.0 <- lmer(perc_cartregen_length ~ Slide_per + AgeCat + (Slide_per | AnimalID),
               data = cartregen2, control=lmerControl(optimizer="bobyqa"))

cper.1 <- lmer(perc_cartregen_length ~ Slide_per + AgeCat + Slide_per*AgeCat + (Slide_per | AnimalID),
               data = cartregen2, control=lmerControl(optimizer="bobyqa"))

anova(cper.base, cper.0, cper.1)
anova(cper.0)
summary(cper.0)
report(cper.0)

#the model without the interaction is the best. It indicates that generally, cartilage % is decreasing from proximal to distal, and that ≥ 22mo have less cartilage % than 3-4mo
#can we redo the analysis to make proximal to distal continuous?
```

## cartilage position analysis as proximal, middle, distal continuous
```{r}
cartregen2 <- cartregen2 %>% 
  mutate(Position2 = case_when(Position == "Proximal" ~ 1,
                               Position == "Middle" ~ 2,
                               Position == "Distal" ~ 3))

cpos.base <- lmer(perc_cartregen_length ~ Position2 + (Position2 | AnimalID), data = cartregen2, control=lmerControl(optimizer="bobyqa"))

cpos.0 <- lmer(perc_cartregen_length ~ Position2 + AgeCat + (Position2 | AnimalID),
               data = cartregen2, control=lmerControl(optimizer="bobyqa"))

cpos.1 <- lmer(perc_cartregen_length ~ Position2 + AgeCat + Position2*AgeCat + (Position2 | AnimalID),
               data = cartregen2, control=lmerControl(optimizer="bobyqa"))

anova(cpos.base, cpos.0, cpos.1)
anova(cpos.0)
summary(cpos.0)

#only position is significant, so simplified model and showed effect of cartilage percent decreasing with position
```

## cartilage count graph
```{r}
ccountplot <- ggplot(cartregen_means, aes(AgeCat, mean_count)) +
  geom_bar(aes(fill = AgeCat), fun = "mean", stat = "summary", alpha = 0.8, width = 0.75) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  geom_point2(size = 2, alpha = 0.6, color = "black") +
  ylab("Mean Number of \nCartilage Pieces in ROI") + xlab("") +
  #scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = c(2,4,6,8,10,12), limits = c(0,12)) +
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") +
  theme(legend.position = "none", axis.text.x=element_text(angle=45, vjust = 1, hjust = 1))
ccountplot
ggsave("Figures/CartilageCount.pdf", dpi=300, width=40, height=45, unit="mm")
```

## cartilage count analysis
```{r}
#oneway anova, taking the mean count for each animal across all slides/positions
res_aov <- aov(mean_count ~ AgeCat, data = cartregen_means)
summary(res_aov)
report(res_aov)
TukeyHSD(res_aov)
```
## cartilage count position (proximal, middle, distal) graph
```{r}
ccountposplot <- ggplot(cartregen2, aes(AgeCat, Count.x, fill = Position_Age)) +
  geom_boxplot(alpha = 0.85) +
  #geom_bar(fun = "median", stat="summary", position = "dodge", color = "black", alpha = 0.85) +
  #stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  #geom_point2(size = 2, alpha = 0.5, position = position_dodge(width=.9)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = c(0,2,4,6,8,10,12)) +
  ylab("Number of \nCartilage Pieces in ROI") + xlab("") +
  guides(color = "none") +
  scale_fill_manual(values = c("#440154", "#e57efd", "#f5cbfe",
                               "#5ec962", "#99dd9b", "#d4f0d5",
                               "#21918c", "#90e6e2", "#d0f4f3",
                               "#3b528b", "#a0b0d7", "#d7deee")) +
  theme_cowplot() + theme(legend.position = "none")
ccountposplot 

ccountposplot2 <- ggplot(cartregen2, aes(Position, Count.x, color = AgeCat, group = AgeCat)) +
  stat_summary(geom = "line", fun = "median", position = position_dodge(width = 0.4), linetype = "dashed") +
  stat_summary(fun.min = function(z) { quantile(z,0.25) },
  fun.max = function(z) { quantile(z,0.75) },
  fun = median, position = position_dodge(width = 0.4), shape = 3, size = 1) +
  geom_point2(size = 2, alpha = 0.6, position = position_dodge(width = 0.4)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = c(2,4,6,8,10,12), limits = c(0,12)) +
  ylab("Number of \nCartilage Pieces in ROI")  + xlab("") + labs(color = "Age \nat Injury", shape = "Age \nat Injury") +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") + theme(legend.position = "none")
ccountposplot2
ggsave("Figures/CartilageCount_position.pdf", width=80, height=45, unit="mm", dpi = 300)
```
```{r}
ggplot(cartregen, aes(Slide_per, Count.x, color = AgeCat)) +
  geom_point() +
  facet_wrap(~AnimalID)
```


## cartilage count position analysis as proximal, middle, distal continuous
```{r}
ccpos.base <- lmer(Count.x ~ Position2 + (Position2 | AnimalID), data = cartregen2, control=lmerControl(optimizer="bobyqa"))

ccpos.0 <- lmer(Count.x ~ Position2 + AgeCat + (Position2 | AnimalID),
               data = cartregen2, control=lmerControl(optimizer="bobyqa"))

ccpos.1 <- lmer(Count.x ~ Position2 + AgeCat + Position2*AgeCat + (Position2 | AnimalID),
               data = cartregen2, control=lmerControl(optimizer="bobyqa"))

anova(ccpos.base, ccpos.0, ccpos.1)
anova(ccpos.base)
summary(ccpos.base)

#nothing is significant in any model, which better represents the graph. Also, technically the graph should be individual lines to show the random effect, but that might look too confusing.
```

## Cartilage panel graph
```{r}
plot_grid(cmeansplot, cposplot2,
          ccountplot, ccountposplot2,
          ncol = 2, rel_widths = c(1,2,1,2),  labels = NULL)
ggsave("Figures/CartilagePanel.png", dpi = 300, width = 100, height = 80, unit = "mm")
```


## adipocyte graph
```{r}
adipo_means <- adipo_means %>% 
  mutate(AgeCat2 = case_when(AgeCat == "Uninj. Tissue" ~ 1,
                             AgeCat == "3-4mo" ~ 0,
                             AgeCat == "4-6mo" ~ 0,
                             AgeCat == "6-9mo" ~ 0,
                             AgeCat == "≥ 22mo" ~ 0))


acountplot <- ggplot(adipo_means, aes(AgeCat, mean_count_area, fill = AgeCat)) +
  geom_boxplot(alpha = 0.8)+
  geom_point2(size = 1, alpha = 0.6, color = "black") +
  ylab("Mean Adipocytes \nper 100µM") + xlab("") +
  #scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = c(0,2,4,6,8,10,12,14,16,18,20), limits = c(0,20)) +
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") +
  theme(legend.position = "none", axis.text.x=element_text(angle=45, vjust = 1, hjust = 1))
acountplot
ggsave("Figures/AdipoCount.pdf", dpi=300, width=40, height=45, unit="mm")
```

## adipocyte analysis
```{r}
library(FSA)
#kruskal wallis, taking the mean count for each animal across all slides/positions
hist(adipo_means$mean_count_area)
kruskal.test(mean_count_area ~ AgeCat, data = adipo_means)
dunnTest(mean_count_area ~ AgeCat, data = adipo_means, method = "hochberg")
```
## adipocyte position graph
```{r}
adiporegen2 <- adiporegen %>% 
  mutate(Position = case_when(Slide_per <= 33.333 ~ "Proximal",
                              Slide_per > 33.333 & Slide_per < 66.666 ~ "Middle",
                              Slide_per >= 66.666 ~ "Distal")) %>% 
  filter(AgeCat != "Uninj. Tissue") %>% 
  mutate(Position_Age = paste(AgeCat, Position, sep = "-")) %>%
  mutate(Position2 = case_when(Position == "Proximal" ~ 1,
                              Position == "Middle" ~ 2,
                              Position == "Distal" ~ 3)) 
adiporegen2$Position <- factor(adiporegen2$Position, levels = c("Proximal", "Middle", "Distal"))

aposplot <- ggplot(adiporegen2, aes(AgeCat, count_area, fill = Position_Age)) +
  geom_boxplot(alpha = 0.85) +
  #geom_bar(fun = "median", stat="summary", position = "dodge", color = "black", alpha = 0.85) +
  #stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  #geom_point2(size = 2, alpha = 0.5, position = position_dodge(width=.9)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  ylab("Mean Number of Adipocytes \nper 100µM")  + xlab("") +
  guides(color = "none") +
  scale_fill_manual(values = c("#440154", "#e57efd", "#f5cbfe",
                               "#5ec962", "#99dd9b", "#d4f0d5",
                               "#21918c", "#90e6e2", "#d0f4f3",
                               "#3b528b", "#a0b0d7", "#d7deee")) +
  theme_cowplot() + theme(legend.position = "none")
aposplot

aposplot2 <- ggplot(adiporegen2, aes(Position, count_area, color = AgeCat, group = AgeCat)) +
  stat_summary(geom = "line", fun = "median", position = position_dodge(width = 0.4), linetype = "dashed") +
  stat_summary(fun.min = function(z) { quantile(z,0.25) },
  fun.max = function(z) { quantile(z,0.75) },
  fun = median, position = position_dodge(width = 0.4), shape = 3) +
  geom_point2(alpha = 0.6, position = position_dodge(width = 0.4)) +
  scale_y_continuous(breaks = c(2,4,6,8,10)) +
  scale_y_break(breaks = c(11, 14), scales = 0.15, ticklabels = c(15,30)) +
  ylab("Median Adipocytes \nper 100µM")  + xlab("") + labs(color = "Age \nat Injury") +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") + theme(legend.position = "none")
aposplot2
ggsave("Figures/AdipoCount_position_wo_scalebreak.pdf", dpi=300, width=80, height=45, unit="mm")
```
```{r}
 ggplot(adiporegen, aes(Slide_per, count_area, color = AgeCat)) +
  geom_point() +
  facet_wrap(~AnimalID)
```


## adipocyte count position analysis as proximal, middle, distal continuous
```{r}
apos.base <- lmer(count_area ~ Position2 + (Position2 | AnimalID), data = adiporegen2, control=lmerControl(optimizer="bobyqa"))
apos.0 <- lmer(count_area ~ Position2 + AgeCat + (Position2 | AnimalID), data = adiporegen2, control=lmerControl(optimizer="bobyqa"))
apos.1 <- lmer(count_area ~ Position2 + AgeCat + Position2*AgeCat + (Position2 | AnimalID), data = adiporegen2, control=lmerControl(optimizer="bobyqa"))

anova(apos.base, apos.0, apos.1)
anova(apos.1)
summary(apos.1)
```

## muscle fiber graph
```{r}
muscle_means <- muscle_means %>% 
  mutate(AgeCat2 = case_when(AgeCat == "Uninj. Tissue" ~ 1,
                             AgeCat == "3-4mo" ~ 0,
                             AgeCat == "4-6mo" ~ 0,
                             AgeCat == "6-9mo" ~ 0,
                             AgeCat == "≥ 22mo" ~ 0))

mcountplot <- ggplot(muscle_means, aes(AgeCat, mean_count_area)) +
  geom_boxplot(aes(fill = AgeCat), alpha = 0.8) +
  geom_point2(size = 1, alpha = 0.6, color = "black") +
  ylab("Mean Muscle Fibers \nper 100µM") + xlab("") +
  #scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  #scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = c(2,4,6,8,10,12,14,16,18,20), limits = c(0,20)) +
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") +
  theme(legend.position = "none", axis.text.x=element_text(angle=45, vjust = 1, hjust = 1))
mcountplot
ggsave("Figures/MuscleCount.pdf", dpi=300, width=40, height=45, unit="mm")
```
## muscle analysis
```{r}
#kruskal wallis, taking the mean count for each animal across all slides/positions
hist(muscle_means$mean_count_area)
kruskal.test(mean_count_area ~ AgeCat, data = muscle_means)
dunnTest(mean_count_area ~ AgeCat, data = muscle_means, method = "holm")
```
## muscle position graph
```{r}
muscleregen2 <- muscleregen %>% 
  mutate(Position = case_when(Slide_per <= 33.333 ~ "Proximal",
                              Slide_per > 33.333 & Slide_per < 66.666 ~ "Middle",
                              Slide_per >= 66.666 ~ "Distal")) %>% 
  filter(AgeCat != "Uninj. Tissue") %>% 
  mutate(Position_Age = paste(AgeCat, Position, sep = "-")) %>%
  mutate(Position2 = case_when(Position == "Proximal" ~ 1,
                              Position == "Middle" ~ 2,
                              Position == "Distal" ~ 3))
muscleregen2$Position <- factor(muscleregen2$Position, levels = c("Proximal", "Middle", "Distal"))

mposplot <- ggplot(muscleregen2, aes(AgeCat, count_area, fill = Position_Age)) +
  geom_boxplot(alpha = 0.85) +
  #geom_bar(fun = "median", stat="summary", position = "dodge", color = "black", alpha = 0.85) +
  #stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  #geom_point2(size = 2, alpha = 0.5, position = position_dodge(width=.9)) +
  ylab("Mean Number of Muscle Fibers \nper 100µM")  + xlab("") +
  guides(color = "none") +
  scale_fill_manual(values = c("#440154", "#e57efd", "#f5cbfe",
                               "#5ec962", "#99dd9b", "#d4f0d5",
                               "#21918c", "#90e6e2", "#d0f4f3",
                               "#3b528b", "#a0b0d7", "#d7deee")) +
  theme_cowplot() + theme(legend.position = "none")
mposplot

mposplot3 <- ggplot(muscleregen2, aes(Position, count_area, color = AgeCat, group = AgeCat)) +
  stat_summary(geom = "line", fun = "median", position = position_dodge(width = 0.4), linetype = "dashed") +
  stat_summary(fun.min = function(z) { quantile(z,0.25) },
  fun.max = function(z) { quantile(z,0.75) },
  fun = median, position = position_dodge(width = 0.4),
  shape = 3) + 
  geom_point2(alpha = 0.6, position = position_dodge(width = 0.4)) +
  scale_y_break(breaks = c(5, 5.5), scales = 0.15, ticklabels = c(6,12)) +
  ylab("Median Muscle Fibers \nper 100µM")  + xlab("") + labs(color = "Age \nat Injury") +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") + theme(legend.position = "none")
mposplot3
ggsave("Figures/MuscleCount_position.pdf", dpi=300, width=80, height=45, unit="mm")

#significant effect graph
mposplot2 <- ggplot(muscleregen2, aes(Position, count_area, fill = Position)) +
  #geom_point2(size = 2, alpha = 0.5) +
  stat_summary(fun.min = function(z) { quantile(z,0.25) },
  fun.max = function(z) { quantile(z,0.75) },
  fun = median, position = position_dodge(width = 0.2)) +
  stat_summary(fun = "median", geom = "path", mapping = aes(group = -1), linetype = "dashed") +
  #scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = c(0,2,4,6,8,10,12), limits = c(0,12)) +
  ylab("Mean Number of Muscle Fibers \nper 100µM") + xlab("Age at Injury") +
  guides(color = "none") +
  scale_fill_viridis_d() +
  theme_cowplot() + theme(legend.position = "none")
mposplot2
```
```{r}
ggplot(muscleregen, aes(Slide_per, count_area, color = AgeCat)) +
  geom_point() +
  facet_wrap(~AnimalID)
```


## muscle count position analysis as proximal, middle, distal continuous
```{r}
mpos.base <- lmer(count_area ~ Position2 + (Position2 | AnimalID), data = muscleregen2, control=lmerControl(optimizer="bobyqa"))
mpos.0 <- lmer(count_area ~ Position2 + AgeCat + (Position2 | AnimalID), data = muscleregen2, control=lmerControl(optimizer="bobyqa"))
mpos.1 <- lmer(count_area ~ Position2 + AgeCat + Position2*AgeCat + (Position2 | AnimalID), data = muscleregen2, control=lmerControl(optimizer="bobyqa"))

anova(mpos.base, mpos.0, mpos.1)
anova(mpos.base)
summary(mpos.base)

#nothing is significant in any model, which better represents the graph. Also, technically the graph should be individual lines to show the random effect, but that might look too confusing.
```
## hair follicle graph
```{r}
hairs_means <- hairs_means %>% 
  mutate(AgeCat2 = case_when(AgeCat == "Uninj. Tissue" ~ 1,
                             AgeCat == "3-4mo" ~ 0,
                             AgeCat == "4-6mo" ~ 0,
                             AgeCat == "6-9mo" ~ 0,
                             AgeCat == "≥ 22mo" ~ 0))

hcountplot <- ggplot(hairs_means, aes(AgeCat, mean_count_area)) +
  geom_boxplot(aes(fill = AgeCat), alpha = 0.8)+
  geom_point2(size = 1, alpha = 0.6, color = "black") +
  ylab("Mean Hairs \nper 100µM") + xlab("") +
  #scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  #scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = c(2,4,6,8,10,12,14,16,18,20), limits = c(0,20)) +
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") +
  theme(legend.position = "none", axis.text.x=element_text(angle=45, vjust = 1, hjust = 1))
hcountplot
ggsave("Figures/HairCount.pdf", dpi=300, width=40, height=45, unit="mm")
```
## hair analysis
```{r}
hist(hairs_means$mean_count_area)
#kruskal wallis, taking the mean count for each animal across all slides/positions
kruskal.test(mean_count_area ~ AgeCat, data = hairs_means)
dunnTest(mean_count_area ~ AgeCat, data = hairs_means, method = "holm")
```
## hairs position graph
```{r}
hairregen2 <- hairregen %>% 
  mutate(Position = case_when(Slide_per <= 33.333 ~ "Proximal",
                              Slide_per > 33.333 & Slide_per < 66.666 ~ "Middle",
                              Slide_per >= 66.666 ~ "Distal")) %>% 
  filter(AgeCat != "Uninj. Tissue") %>% 
  mutate(Position_Age = paste(AgeCat, Position, sep = "-")) %>%
  mutate(Position2 = case_when(Position == "Proximal" ~ 1,
                              Position == "Middle" ~ 2,
                              Position == "Distal" ~ 3)) 
hairregen2$Position <- factor(hairregen2$Position, levels = c("Proximal", "Middle", "Distal"))

hposplot <- ggplot(hairregen2, aes(AgeCat, count_area, fill = Position_Age)) +
  geom_boxplot(alpha = 0.85) +
  #geom_bar(fun = "median", stat="summary", position = "dodge", color = "black", alpha = 0.85) +
  #stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  #geom_point2(size = 2, alpha = 0.5, position = position_dodge(width=.9)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  ylab("Mean Number of Hairs \nper 100µM")  + xlab("") +
  guides(color = "none") +
  scale_fill_manual(values = c("#440154", "#e57efd", "#f5cbfe",
                               "#5ec962", "#99dd9b", "#d4f0d5",
                               "#21918c", "#90e6e2", "#d0f4f3",
                               "#3b528b", "#a0b0d7", "#d7deee")) +
  theme_cowplot() + theme(legend.position = "none")


hposplot2 <- ggplot(hairregen2, aes(Position, count_area, color = AgeCat, group = AgeCat)) +
  stat_summary(geom = "line", fun = "median", position = position_dodge(width = 0.4), linetype = "dashed") +
  stat_summary(fun.min = function(z) { quantile(z,0.25) },
  fun.max = function(z) { quantile(z,0.75) },
  fun = median, position = position_dodge(width = 0.4),
  shape = 3) + 
  geom_point2(alpha = 0.6, position = position_dodge(width = 0.4)) +
  scale_y_break(breaks = c(1.67,1.68), scale = 0.25, ticklabels = c(1.7, 2.0)) +
  ylab("Median Number of Hairs \nper 100µM")  + xlab("") + labs(color = "Age \nat Injury") +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#D55E00")) +
  theme_cowplot(font_size = 8, font_family = "Arial") + theme(legend.position = "none")
hposplot2
ggsave("Figures/HairCount_position.pdf", dpi=300, width=80, height=45, unit="mm")
```
```{r}
ggplot(hairregen, aes(Slide_per, count_area, color = AgeCat)) +
  geom_point() +
  facet_wrap(~AnimalID)
```


## hair position analysis
```{r}
hpos.base <- lmer(count_area ~ Position2 + (Position2 | AnimalID), data = hairregen2, control=lmerControl(optimizer="bobyqa"))
hpos.0 <- lmer(count_area ~ Position2 + AgeCat + (Position2 | AnimalID), data = hairregen2, control=lmerControl(optimizer="bobyqa"))
hpos.1 <- lmer(count_area ~ Position2 + AgeCat + Position2*AgeCat + (Position2 | AnimalID), data = hairregen2, control=lmerControl(optimizer="bobyqa"))

anova(hpos.base, hpos.0, hpos.1)
anova(hpos.base)
summary(hpos.base)

```

## amh panel
```{r}
plot_grid(acountplot, aposplot2 + theme(legend.position = "none"),
          mcountplot, mposplot3 + theme(legend.position = "none"),
          hcountplot, hposplot2 + theme(legend.position = "none"),
          ncol = 2, labels = NULL)
ggsave("Figures/AMHPanel.png", dpi = 300, width = 134, height = 150, unit = "mm")
```




